### 2017-04-07 Paper01_EnthalpyAndCrystallization.tex
Method - refined first paragraph

The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a continuous circulating Ar flow. The alloy was heated and cooled through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500\degree C to ensure homogeneity. Bulk amorphous \MgZnCa~ plate with a thickness of $XX~ \mu m$ was produced by copper mold injection casting. The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to a thickness of $3.25~ mm$.

>>>>

The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured through heating and cooling through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ plate with a thickness of $XX~ \mu m$ was produced by copper mold injection casting. The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25~ mm$.

\gls{dc} magnetron sputtering
